Karbowski model in 2-D

### 2020-05-19 paper/supplementary/supp.tex
Some more notes on the Post-eLife review work

Let $\hat{a}_i$ be the sum of the branching densities of all axon
types except $i$.
%
\begin{equation}
\hat{a}_i(\mb{x},t) = \sum_{p\ne i}^N a_p(\mb{x},t)
\end{equation}
%
Define the static vector field $\mb{g}$ as:
%
\begin{equation} \label{eq:g_i}
\mb{g}_i(\mb{x}) = \sum_{j=1}^M \big(\gamma_{i,j} \nabla\rho_j(\mb{x}) \big)
\end{equation}

@@

Add a term to the Karbowski equations which reduces the branching rate
change based on the proximity of branching of other TC axon types:
%
\begin{equation} \label{eq:dc_compo_1}
\frac{\partial c_i(\mb{x},t)}{\partial t} = -\alpha_i c_i(\mb{x},t)
+ \beta_i n(\mb{x},t)
[a_i(\mb{x},t)]^k
\end{equation}
%
\begin{equation} \label{eq:da_compo_1}
\frac{\partial a_i(\mb{x},t)}{\partial t}
= \nabla\vcdot\mb{J}_i(\mb{x},t) - \frac{\partial
c_i(\mb{x},t)}{\partial t} - \frac{\epsilon_i  a_i}{N-1} \sum_{p \ne i}^{N} a_p(\mb{x}, t)^l
\end{equation}
%
\begin{equation}
n(\mb{x},t) = 1 - \sum_{i=1}^{N} c_i(\mb{x}, t)
\end{equation}
%
with the flux current as given by Eq.~\ref{eq:J} and Neumann
boundary conditions as usual. This adds two parameter sets; $\epsilon$
and $l$. The factor $\frac{1}{N-1}$ ensures that the value of
$\epsilon$ scales with $N$.

@@

%
\begin{equation} \label{eq:dc_comp4}
\frac{\partial c_i}{\partial t} = -\alpha_i c_i
+ \beta_i n
[a_i]^k
\end{equation}
%
\begin{equation} \label{eq:da_comp4}
\frac{\partial a_i}{\partial t}
= \nabla\vcdot\mb{J}_i + \alpha_i c_i - \beta_i n
[a_i]^k - \frac{\epsilon_i}{N-1} a_i \sum_{p \ne i}^{N} a_p^l
\end{equation}
%
\begin{equation} \label{eq:conserve_NM_comp4}
n = 1 - \sum_{i=1}^{N} c_i(\mb{x}, t)
\end{equation}
%
\begin{equation} \label{eq:divJExpanded_comp4}
%
\nabla\vcdot\mb{J}_i = D \dvrg a_i
%
- E a_i \dvrg n
- E \nabla n \vcdot \nabla a_i
%
- a_i\nabla\vcdot\mb{g}_i
- \mb{g}_i\vcdot\nabla a_i
%
\end{equation}

@@

The mechanism works quite nicely, and has the advantage of using only
graded guidance molecule expression.
See \code{configs/whiskers/5N\_boundedorder.json}
%
% BIBLIOGRAPHY
%
\selectlanguage{English}
\bibliographystyle{abbrvnotitle}
% The bibliography NoTremor.bib is the one exported from Zotero. It
% may be necessary to run my UTF-8 cleanup script, bbl_utf8_to_latex.sh
%%\bibliography{NoTremor}
%
% It produces this:
\begin{thebibliography}{1}

>>>>

Let $\hat{a}_i$ be the sum of the branching densities of all axon
types except $i$.
%
\begin{equation}\label{eq:ahat}
\hat{a}_i(\mb{x},t) = \sum_{j\ne i}^N a_j(\mb{x},t)
\end{equation}
%
Define the static vector field $\mb{g}$ as:
%
\begin{equation} \label{eq:g_i}
\mb{g}_i(\mb{x}) = \sum_{j=1}^M \big(\gamma_{i,j} \nabla\rho_j(\mb{x}) \big)
\end{equation}

@@

Add a term to the Karbowski equations which reduces the branching rate
change based on the proximity of branching of other TC axon types:
%
\begin{equation} \label{eq:dc_compo_1}
\frac{\partial c_i(\mb{x},t)}{\partial t} = -\alpha_i c_i(\mb{x},t)
+ \beta_i n(\mb{x},t)
[a_i(\mb{x},t)]^k
\end{equation}
%
\begin{equation} \label{eq:da_compo_1}
\frac{\partial a_i(\mb{x},t)}{\partial t}
= \nabla\vcdot\mb{J}_i(\mb{x},t) - \frac{\partial
c_i(\mb{x},t)}{\partial t} - \frac{\epsilon_i  a_i}{N-1} \sum_{j \ne i}^{N} a_j(\mb{x}, t)^l
\end{equation}
%
\begin{equation}
n(\mb{x},t) = 1 - \sum_{i=1}^{N} c_i(\mb{x}, t)
\end{equation}
%
with the flux current as given by Eq.~\ref{eq:J} and Neumann
boundary conditions as usual. This adds two parameter sets; $\epsilon$
and $l$. The factor $\frac{1}{N-1}$ ensures that the value of
$\epsilon$ scales with $N$.

@@

%
\begin{equation} \label{eq:dc_comp4}
\frac{\partial c_i}{\partial t} = -\alpha_i c_i
+ \beta_i n
[a_i]^k
\end{equation}
%
\begin{equation} \label{eq:da_comp4}
\frac{\partial a_i}{\partial t}
= \nabla\vcdot\mb{J}_i + \alpha_i c_i - \beta_i n
[a_i]^k - \frac{\epsilon_i}{N-1} a_i \sum_{j \ne i}^{N} (a_j)^l
\end{equation}
%
\begin{equation} \label{eq:conserve_NM_comp4}
n = 1 - \sum_{i=1}^{N} c_i(\mb{x}, t)
\end{equation}
%
\begin{equation} \label{eq:divJExpanded_comp4}
%
\nabla\vcdot\mb{J}_i = D \dvrg a_i
%
- E a_i \dvrg n
- E \nabla n \vcdot \nabla a_i
%
- a_i\nabla\vcdot\mb{g}_i
- \mb{g}_i\vcdot\nabla a_i
%
\end{equation}

@@

The mechanism works quite nicely, and has the advantage of using only
graded guidance molecule expression.
See \code{configs/whiskers/5N\_boundedorder.json}

\section {Post eLife Review work}

One of the reviewers, Bard Ermentrout, suggested an alternative formulation of
the branching competition, to avoid the need to divisively normalize the
branching density at each simulation step.

The suggestion was to let the $\chi$ term from equation 3 from the reviewed
paper be given by:

\begin{equation}\label{eq:chibard}
\chi_i = \frac{a_i}{N-1} \nabla\hat{a_i}
\end{equation}

where $\hat{a}_i$, the sum of branching over all other TC types, is given by
Eq.~\ref{eq:ahat}.

Compare this with Eq.~\ref{eq:J_NM_with_comp} from Section \ref{sec:comp2},
which was one of the competition types I tried fairly early on. In fact, I
think it was about my first idea for competition. It's similar, but not
identical. I passed it over at that stage, because the competition it produced
seemed weak, and I was relying on the development of contours and `well
localized regions' to indicate success. In Eq.~\ref{eq:J_NM_with_comp}, the
additional term is in the expression for $\mb{J}_i$, so the \emph{flux of
branching density for TC type $i$ is a function of the gradient of the
branching of other TC types, $j\ne i$}. Eq.~\ref{eq:chibard} says something
subtly different: \emph{the rate of change of branching density is modulated
by the gradient of branching of other TC types}.

Implementing Eq.~\ref{eq:chibard} gives:

\begin{equation} \label{eq:dabard}
\frac{\partial a_i}{\partial t} = \nabla\vcdot\left(D \nabla a_i-a_i\sum_{j=1}^{M} \gamma_{i,j}\nabla \rho_j(\mb{x})\right) - \frac{\partial c_i}{\partial t} + \frac{a_i}{N-1} \nabla\hat{a_i}.
\end{equation}

in the style of the preprint.

Although I have re-implemented rd\_james\_comp2, which expresses
Eq.~\ref{eq:J_NM_with_comp},and found that it does provide competition enough
to generate a barrel field like ordering, I've not yet implemented Bard's
suggestion precisely, so I think that's up next. However, I imagine that this
may be unstable without the sigmoiding of $a_i$ in the expression for
$\chi_i$.

%
% BIBLIOGRAPHY
%
\selectlanguage{English}
\bibliographystyle{abbrvnotitle}
% The bibliography NoTremor.bib is the one exported from Zotero. It
% may be necessary to run my UTF-8 cleanup script, bbl_utf8_to_latex.sh
%%\bibliography{NoTremor}
%
% It produces this:
\begin{thebibliography}{1}
